### 2021-02-16 Chapter-1/Chapter-1.tex
update

\chapter{Introduction} \label{chapter1:introduction}

@@

On the contrary, software approaches are
usually easy to implement. By removing the above two kinds of code patterns, developers protect their 
code from a seris of side-channel attacks.
Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

Regarding the root cause of software-based side channel attacks, many of them originate
from two specific circumstances: data flow from secrets to load
addresses and data flow from secrets to branch conditions. We refer to them as
 secret-dependent memory-access and control-flow, respectively. A
central problem is eliminating these two code patterns. 
Recent
works~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946},
find plenty of side-channel vulnerabilities. For example,
DATA~\cite{217537} reports 2,246 potential leakage sites for the RSA
implementation in OpenSSL\@. 
%After some inspections, 1,510 leakages are dismissed. But it
%still leaves 460 data-access leakages and 278 control-flow leakages. 
However, we find most of the reported vulnerabilities are not fixed because
of the following reasons.
First, many side-channels vulnerable implementations have better performance.
Those vulnerabilities are well-known for years. For example,
Symmetric encryptions like AES and DES still uses lookup tables (T-tables), which
is fast but notoriously known to be vulnerable to side channels.
As for asymmetric encryptions, most implementations of RSA, adopt the CRT optimization,
which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
Second, side-channels are numerous and it is hard to fix all these vulnerabilities,
let alone the majority of them are negligible. 
That is, some vulnerabilities can result in the key being 
entirely compromised~\cite{184415, aumuller2002fault}, but many other vulnerabilities prove to be less
severe in reality. Therefore, we need a proper quantification metric to 
assess the sensitive level of side-channel vulnerabilities.

Previous attempts like static methods~\cite{182946,5207642}, usually with
abstract interpretations, can give a leakage upper bound, which is useful to
justify the implementation is secure if they report zero or little leakage.
However, they cannot indicate how severe the leakage is because of the
over-approximation method they apply. For example, CacheAudit~\cite{182946} reports that the upper
bound leakage of AES-128 exceeds the original key size! The dynamic methods take
another approach with a concrete input and run the program in a real
environment. Although they are very precise in terms of actual leakages, no
existing tool can precisely assess the severity of the vulnerabilities in production
software.

To overcome these limitations, we propose a novel method to quantify information
leakages precisely. Unlike previous works that only consider the
``average'' information leakage, we study the problem based on real attack
scenarios. The average information leakage model assumes the target program has
\emph{variable} or \emph{random} sensitive information as inputs when an attack is
launched. However, for real-world attacks, an adversary may run the target
problem with the \emph{fixed} unknown sensitive information
as the input. Therefore, the previous threat model cannot model real attack
scenarios. In contrast, our method is more precise and fine-grained. 
We quantify
the amount of leaked information as the cardinality of the set of possible
inputs based on attackers' observations.
Before an attack, an adversary has a large but finite input space. Every time
when the adversary observes a leakage site, he can eliminate some potential
inputs and reduce the size of the input space. The smaller the input space is,
the more information is obtained. In an extreme case, if the size of the
input space reduces to one, the adversary can uniquely determine the input, 
which means all the secret information (e.g., the whole secret key) is
leaked. By counting the number of distinct inputs, we can quantify the
information leakage precisely.

We use constraints generated from symbolic execution to model the relation 
between the original sensitive input
and the attacker's observations. Symbolic execution can
provide fine-grained information but is usually believed to be an expensive
operation in terms of performance. Therefore, existing dynamic symbolic
execution works~\cite{203878,236338,Brotzman19Casym} either only analyze
small programs or apply some domain knowledge~\cite{203878} to simplify the analysis. We
systematically exam the bottleneck of the trace-oriented symbolic execution and optimize it
to be scalable to real-world cryptosystems.

We apply the above technique and build a tool called \tool{},
%\footnote{CleverHans is a horse that can ``count''. Our tool uses an advanced
%%method to count the number of leaked bits from side channels.} 
to discover potential information leakage sites as well as estimate how
many bits they can leak for each leakage site. 
First, we collect dynamic execution traces for each target
libraries and then run symbolic execution on each instruction. In this way, we model
each side-channel leakage as a logic formula. The sensitive input is divided into
several independent bytes, and each byte is regarded as a unique and free symbol. Those
formulas can precisely model side-channel vulnerabilities. Then we use the conjunction
of those formulas to model the same leaks in the source code but appears in the different location of
the execution trace file (e.g., leakages inside a loop).
Finally, we introduce Monte Carlo
sampling method to estimate the single and combined information leakage.

We apply \tool{} on both symmetric and asymmetric ciphers from real-world crypto
libraries, including OpenSSL, mbed TLS and Monocypher\@. The experimental result confirms
that \tool{} can precisely identify previously known vulnerabilities, report
how much information is leaked and which byte in the original sensitive buffer
is leaked. We also test \tool{} on side-channel free algorithms. \tool{} has no
false positives.
Although some of the analyzed crypto libraries have a number of
side-channels, they actually leak very little information. Also, we also show the
of widely deployed software countermeasures can mitigate side channels.
\tool\ also discovers new vulnerabilities. With the help of \tool{}, we confirm
that those vulnerabilities are severe.

In summary, we make the following contributions:

\begin{itemize}
      \item We propose a novel method that can quantify fine-grained leaked
            information from side-channel vulnerabilities to match real attack
            scenarios. Our method is different from previous ones in that we
            model real attack scenarios more precisely, while the previous
            research only models the ``average'' or ``random'' case. 
            We transfer the information quantification problem into a counting
            problem and use the Monte Carlo sampling method to estimate the
            information leakage.
            % compared to previous results and
            %%   We model each side-channel vulnerabilities as math formulas %
            %and mutiple side-channel vulnerabilities can be seen as the %
            %conjunction of those formulas, which precisely models the % program
            %semantics.

      %%\item  Some initial results indicate the sampling
      %%     method suffers from the curse of dimensionality problem. Therefore, we
      %%      design a guided sampling method and provide the
      %%      corresponding error estimate.

      \item We implement the proposed method into a practical tool and apply it
            on several real-world software. \tool{} successfully identifies
            memory-related side-channel vulnerabilities and calculates the
            corresponding information leakage. 
            Our results are surprisingly different, much more useful in practice.
            The information leakage results
            provide detailed information that can help developers to fix the
            reported vulnerabilities.
\end{itemize}

\section{Contribution}

>>>>

\chapter{Introduction} \label{chapter1}

@@

On the contrary, software approaches are
usually easy to implement. The basic idea is to eliminate key-dependent
control-flow transfers and data accesses. By removing the above two kinds of code patterns, developers protect their 
code from a series of side-channel attacks.

However, it is still hard to apply software approaches in practice due to the following reasons.

\begin{itemize}
    \item It is hard to identify side-channel vulnerabilities in real-world software. In general, many side-channel vulnerabilities are low-level problems. Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of original secret inputs. Recent work can identify side-channel leakages. But those tools can only work on small programs or need to apply some domain knowledge to simplify the analysis. 
    \item Side-channel vulnerabilities are ubiquitous. While some vulnerabilities can result in the key being entirely compromised, many other vulnerabilities are hard to exploit. Moreover, some vulnerable implementations perform better. Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.  
\end{itemize}

\section{Contribution}
To address the above problems, we make the following contributions in this dissertations:

\begin{itemize}
    \item We propose a novel method that can quantify fine-grained leaked
    information from side-channel vulnerabilities that result from actual attack
    scenarios in a single trace attack. Our approach differs from previous ones in that we
    model real attack scenarios for one execution. 
    We model the information quantification problem as a counting problem 
    and use a Monte Carlo sampling method to estimate the information leakage.
    \item We implement the method into a tool and apply it
    to several pieces of real software. \tool{} successfully identifies
    previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. 
    Our results are useful in practice.
    The leakage estimates and the corresponding trigger inputs can 
    help developers to triage and fix the vulnerabilities.
    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically. Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. The method can combine multiple leakage sites to retrieve more information as well.
    \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. We propose a method that can estimate the lower bound of information leakages. The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
\end{itemize}

### 2021-02-16 Chapter-2/Chapter-2.tex
update

\chapter{Background and Related Work}

@@

For example, cached-based
side-channels~\cite{yarom2017cachebleed,191010,184415,,Osvik2006,liu2015last,184415,liu2015last}
rely on the time difference between cache misses and cache hits. We introduce two
common attack strategies, namely Prime+Probe~\cite{liu2015last} and
Flush+Reload~\cite{184415}. Prime+Probe targets a single cache set. An
attacker preloads the cache set with its own data and waits until the victim
executes the program. If the victim accesses the cache set and evicts part of
the data, the attacker will experience a slow measurement. 
While Flush+Reload targets a
single cache line, it requires the attacker and victim share some memory. 
During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who will load the sensitive information to the cache line. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information.
Some other types of side-channels target different hardware
layers other than CPU cache. For example, the controlled-channel
attack~\cite{7163052}, where an attacker works in the kernel space, can infer
sensitive data in shielding systems by observing the page fault sequences
after restricting some code and data pages.

@@

     \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
      \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};    
      \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};    
      \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
      \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};

      \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
      \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
      \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
      \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};

>>>>

\chapter{Background and Related Work}\label{chapter2}

@@

For example, cached-based
side-channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415}
rely on the time difference between cache misses and cache hits. We introduce two
common attack strategies, namely Prime+Probe~\cite{liu2015last} and
Flush+Reload~\cite{184415}. Prime+Probe targets a single cache set. An
attacker preloads the cache set with its own data and waits until the victim
executes the program. If the victim accesses the cache set and evicts part of
the data, the attacker will experience a slow measurement. 
While Flush+Reload targets a
single cache line, it requires the attacker and victim share some memory. 
During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who will load the sensitive information to the cache line. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information.
Some other types of side-channels target different hardware
layers other than CPU cache. For example, the controlled-channel
attack~\cite{7163052}, where an attacker works in the kernel space, can infer
sensitive data in shielding systems by observing the page fault sequences
after restricting some code and data pages.

@@

     \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
      \node[ele,label=left:{\normalsize $k_1$}] (a1) at (0,4) {};    
      \node[ele,label=left:{\normalsize $k_2$}] (a2) at (0,3) {};    
      \node[ele,label=left:{\normalsize $k_3$}] (a3) at (0,2) {};
      \node[ele,label=left:{\normalsize $k_4$}] (a4) at (0,1) {};

      \node[ele,,label=right:{\normalsize $o_1$}] (b1) at (4,4) {};
      \node[ele,,label=right:{\normalsize $o_2$}] (b2) at (4,3) {};
      \node[ele,,label=right:{\normalsize $o_3$}] (b3) at (4,2) {};
      \node[ele,,label=right:{\normalsize $o_4$}] (b4) at (4,1) {};
